---
title: "Example Report"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(knitr)
```

```{r data_load_in, echo = FALSE}
# Master Data===
survey_data <- readRDS("../data/master_data.rds") %>%
  clean_names() %>%
  mutate("Participant ID" = as.character(row_number())) %>% #Making up an ID number for each person
  rename("Reported Age" = "how_old_are_you") %>% #Renaming vars for easier plots/RMD
  relocate("Participant ID", .before = "Reported Age") %>% #I'm just anal about IDs being first
  mutate(`Reported Age` = factor(`Reported Age`, levels = c("Under 18", "18-24", "25-34", "35-44", "45-54", "55-64", "Over 65"))) %>%
  select(c("Participant ID", "Reported Age"))
  

#Games Data===
games_data <- readRDS("../data/new_data_games.rds")

#Music/Artist Data===
artists <- readRDS("../data/fav_artists.rds")

```

## About
This is an super scientific document that explores super accurate data about age, affinity for video games, and music among willing participants!

## Participant Demographics
The only demographic variable that was recorded was age range.

```{r age_range_table, echo = FALSE}
survey_data %>%
  kable()
```

## Affinity for Games
We asked everyone if they liked video games or not. Here are the results:

```{r games_viz, echo=FALSE}
games_viz <- readRDS("plots/game_viz.rds")
games_viz
```

## Affinity for Music
Finally, we asked everyone who there favorite artists were. People stated their favorites were `r combine_words(artists)`. Which shows us some variation between genres.
